---
title: "Assignment 2"
author: "jia en"
date: "2023-10-27"
output: html_document
---
### Load the library

Install the `rvest`package if it is not yet installed
```{r}
if (!("rvest" %in% installed.packages())) {
  install.packages("rvest")
}
library(rvest) 
``` 

### Get the csv example 

Load in the html
Visit the website, read the entire webpage and store them in a html object. 
```{r}
web_html <- read_html ("https://en.wikipedia.org/wiki/Comma-separated_values")
```
Get the csv examples under the header "Example"
Locate the data that we need from the html page.
It is under the section "Example", with id='Example' (which is '.'). 
From there, find the <pre> tags, and scrap the text within the tags.  
```{r}
data_list <- 
  web_html %>%
  html_nodes(xpath='//h2[contains(.,"Example")]//following-sibling::pre') %>%
  html_text()
``` 

Have a look of the tables : 
```{r}
data_list
```


The first element is what we want.  
```{r}
data <- data_list[1]
data
```
### Save the csv example into a csv file
```{r}
write.table(data, file = "car.csv", quote = FALSE, col.names = FALSE, row.names = FALSE)
```

Reload the csv data from the file to make sure the data was saved properly.
```{r}
 read.csv("car.csv")
``` 